A large-scale analysis of racial disparities in police stops across the

### 2019-03-13 lib/paper_results.Rmd
progress

\newpage
\begin{center}
\section{Disparity Analysis}
\end{center}
\begin{center}
\subsection{Outcome test results}
\end{center}
```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$city$outcome$plots$aggregate
```
\newpage
```{r disparity-state-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$state$outcome$plots$aggregate
```

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$plots$aggregate
```
\newpage
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$plots$aggregate
```

>>>>

\newpage
\begin{center}
\section{Disparity Analysis}
\end{center}
\begin{center}
\subsection{Outcome test results}
\end{center}
```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$city$outcome$plots$aggregate
```
```{r disparity-state-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$state$outcome$plots$aggregate
```

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$plots$aggregate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$plots$aggregate
```
